---
title: "Association Analysis"
author: "Paul Ndirangu"
date: "July 26, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
# We first we install the required arules library 
#
install.packages("arules")

# Loading the arules library
#
library(arules)
```

## Loading the dataset.
```{r}
# Loading our Supermarket's dataset from our csv file
# ---
path<-"D:/Moringa/Class/R/IP/IP Week 14/Independent Project/Association Analysis/Supermarket_Sales_Dataset II.csv" 

Dataset<-read.transactions(path, sep=',')

head(Dataset, 10)
View(Dataset)
```

```{r}
# Verifying the object's class
# ---
# This should show us transactions as the type of data that we will need
# ---
# 
class(Dataset)
```

```{r}
# If we wanted to preview the items that make up our dataset,
# alternatively we can do the following
# ---
# 
items<-as.data.frame(itemLabels(Dataset))
colnames(items) <- "Item"
head(items, 10) 

# distribution of the item sets (no. of items purchased in each transaction), etc.
# ---
# 
summary(Dataset)
dev.off()
```

```{r}
# some operation in percentage terms of the total transactions 
# 
itemFrequency(Dataset[, 40:50],type = "absolute")
round(itemFrequency(Dataset[, 40:50],type = "relative")*100,2)

# Displaying top 10 most common items in the transactions dataset 
# and the items whose relative importance is at least 10%
# 
par(mfrow = c(1, 2))

# plot the frequency of items
itemFrequencyPlot(Dataset, topN = 10,col="darkgreen")
itemFrequencyPlot(Dataset, support = 0.01,col="darkred")
```
We observe the frequencies of various products with french fries having the highest value(1282) for the top ten products.


## Implementing the Solution
```{r}
# Building a model based on association rules 
# using the apriori function 
# ---
# We use Min Support as 0.001 and confidence as 0.8
# ---
# 
rules <- apriori (Dataset, parameter = list(supp = 0.001, conf = 0.8))
rules
```
We acheive a total of 74 rules using a confidence level of 0.8 and a support of 0.001


```{r}
# ---
# 
summary(rules)

# Observing rules built in our model i.e. first 5 model rules
# ---
# 
inspect(rules[1:5])


# Interpretation of the first rule:
# ---
# If someone buys frozen smoothie, they are 88.9% likely to buy mineral water.
```
Inspecting the first 5 rules we notice that for rule 1, if a customer buys frozen smoothie or spinach, The are more likely to buy Mineral Water.
This is supported by a confidence level of 88.9% and a support of 0.001066524.


```{r}
# We can also use different criteria such as: (by = "lift" or by = "support")
# 
rules<-sort(rules, by="confidence", decreasing=TRUE)
inspect(rules[1:5])
```
Using confidence as the criteria we get the first rule as;
If a customer buys French Fries, Mushroom cream sauce or pasta, they 
were more likely to buy escalope. 
This is backed by a confidence level of 100% and a support of 0.001066524